Quasi-Monte Carlo Methods: What, Why, and How?

### 2025-06-10 response_letter.tex

We thank the reviewers for their careful reading of the manuscript and for their thoughtful suggestions, which have helped improve both the content and presentation of the work. All grammatical errors and typographical mistakes have been corrected. Below, we provide responses to all comments; substantial changes are highlighted in blue in the revised manuscript

\section*{Response to Reviewer 1}

\begin{response}{1.}
It is unavoidable that surveys of this type are not comprehensive and will choose to focus
on some areas and ignore others. It would be useful to mention something along those lines
somewhere in the introduction.
\end{response}
Good point. Sentence added at the end of the introduction.

\begin{response}{2.}
...This is an unusual way to define a digital
sequence....
\end{response}
We choose this ``unusual'' way because we want to show the connection to the van der Corput sequence.  Lattice sequences, digital sequences, and Halton sequences all can be considered extensions of van der Corput.

By stating that $\bsx^{\text{dig}}_1, \bsx^{\text{dig}}_2, \ldots$ are carefully chosen, we were unintentionally vague, and have now stated that $\bsx^{\text{dig}}_1, \bsx^{\text{dig}}_2, \bsx^{\text{dig}}_4, \bsx^{\text{dig}}_8, \ldots$ are carefully chosen.

Thanks to the reviewer for pointing out the error in our correspondence between generator matrices and the $\boldsymbol{x}_{2^m}$ for $m =  0, 1, \ldots$.  That has been corrected.  These paragraphs have also been reworded.

\begin{response}{3.}
...the definition of a digital sequence also requires segments between powers of $2$ to be nets with parameter (at most) $t$. This also brings a minor point: especially when defining a $(t, d)$-sequence, one does not usually assume that the t parameter applies as the exact $t$ for all segments...
\end{response}
This has been corrected.  Thank you.

### 2025-06-10 HickernellMCQMC2024_QMCTutorial_rev_1.tex
Updates from Overleaf

%%Fred's temporary macros
\newcommand{\FJHNote}[1]{{\textcolor{blue}{Fred: #1}}}
\newcommand{\NKNote}[1]{{\textcolor{blue}{Nathan: #1}}}
\newcommand{\AGSNote}[1]{{\textcolor{blue}{Aleksei: #1}}}
%\usepackage[normalem]{ulem}

@@

This tutorial describes what qMC is, why we would want to use qMC, and how qMC can be implemented well.  The next section illustrates by example the advantages of qMC.  This is followed by a description of how deterministic LD sequences are constructed (Section \ref{sec:construct}) and randomizations that preserve their low-discrepancy (Section \ref{sec:random}).  We describe various measures of discrepancy (Section \ref{sec:discrepancy}).  We explain how to decide what sample size, $n$, is sufficient to meet the user's error requirements (Section \ref{sec:stop}).  We then discuss how to rewrite the problem of interest in a qMC-friendly way (Section \ref{sec:reformulate}). We briefly discuss applications of qMC beyond computing the mean (Section \ref{sec:beyond}), and finish with a short conclusion (Section \ref{sec:conclusion}). \NKNote{Inevitably, this tutorial is not comprehensive of the full breadth of over a century of development in qMC and uniform distribution theory, dating back to Hermann Weyl's seminal 1916 paper \cite{Wey16}. Instead, our goal is to provide a solid foundation in the core concepts along with practical guidance, and to spark further interest and study in the field.}

@@

Another family of LD sequences that is a generalization of the van der Corput sequence \eqref{eq:vdc} is digital sequences \cite{DicPil10a,Nie92}.  For simplicity, we restrict ourselves to $b = 2$ and let $\oplus$ denote binary digitwise addition modulo $2$ (also known as digitwise exclusive or), e.g., $3/8 \oplus 3/4 = {}_20.011 \oplus {}_20.110 = {}_20.101 = 5/8$.  A digital sequence is defined as
\begin{equation} \label{eq:digital}
	\bsx_i^{\text{dig}} := i_0 \bsx^{\text{dig}} _1 \oplus i_1 \bsx^{\text{dig}}_2 \oplus i_2 \bsx^{\text{dig}} _4 \oplus \cdots \in [0,1)^d \quad \text{for }
	i = i_0 + i_12 + i_2 2^2 + \cdots,
\end{equation}
where $\bsx^{\text{dig}}_1, \bsx^{\text{dig}}_2, \ldots$ are carefully chosen.  (For $d=1$ and $x^{\text{dig}}_{2^m} = 2^{-m-1}$, this is the van  der Corput sequence in base $2$.) The node set $\{ \bsx^{\text{dig}}_0, \ldots, \bsx^{\text{dig}}_{2^m-1}\}$  for non-negative integer $m$ is called a digital net and is closed under $\oplus$.

If $x^{\text{dig}}_{ij\ell}$ denotes the $\ell^{\text{th}}$ digit of the $j^{\text{th}}$ coordinate of $\bsx^{\text{dig}}_i$, then the literature often defines generating matrices, $\mathsf{C}_j = \bigl(x^{\text{dig}}_{ij\ell}\bigr)_{\ell,i = 1}^{M,N}$ for $j = 1, \ldots, d$, where $M$ is the maximum number of bits in the expression for $\bsx^{\text{dig}}_i$, say $52$, and $2^N$ is the maximum number of nodes that is intended to be generated.  The digital sequence can then be defined equivalently as
\begin{equation} \label{eq:digitalB}
\renewcommand{\arraystretch}{1.5}
	\begin{pmatrix} x^{\text{dig}}_{ij1} \\ x^{\text{dig}}_{ij2} \\ \vdots \end{pmatrix}
	= \mathsf{C}_j \begin{pmatrix} i_0 \\ i_1 \\ \vdots \end{pmatrix}
    \quad \pmod{2}, \qquad j = 1,\ldots, d, \ i = 0, 1, \ldots.
\end{equation}

To understand how well these nodes are evenly distributed over $[0,1)^d$, imagine a box of the form
\begin{multline} \label{eq:element_box}
	[a_1 b^{-k_1}, (a_1 + 1) 2^{-k_1}) \times \cdots \times [a_d b^{-k_d}, (a_d + 1) 2^{-k_d}), \\
	a_j \in \{0, \ldots, 2^{k_j} - 1\}, \ k_j \in \{0,1, \ldots \}, \qquad j =1, \ldots d, \ \bsk \in \NN_0.
\end{multline}
This box has volume $2^{-(k_1 + \cdots +k_d)} = 2^{-\lVert\bsk\rVert_1}$.  For a digital net with $2^m$ nodes and $\lVert \bsk \rVert_1 \le m$, a ``fair share" of nodes for this box would be $2^{m- \lVert \bsk \rVert_1}$.  This will occur if and only if
\begin{multline} \label{eq:tcond}
	\text{the first $k_1$ rows of the first $m$ columns of $\mathsf{C}_1$ plus} \\
	\text{the first $k_2$ rows of the first $m$ columns of $\mathsf{C}_2$ plus} \\
	 \vdots \\
	\text{the first $k_d$ rows of the first $m$ columns of $\mathsf{C}_d$} \\
	\text{are linearly independent over addition and multiplication modulo $2$, }
\end{multline}
regardless of the choice of $\bsa = (a_1, \ldots, a_d)$.  The $t$-value of a digital net with $2^m$ nodes is defined as the smallest $t$ for which condition \eqref{eq:tcond} holds for all $\bsk$ with $\lVert \bsk \rVert_1 \le m-t$.  Equivalently, this $t$ is the smallest value for which every box of the form \eqref{eq:element_box} with volume $2^{\lVert \bsk \rVert_1 - m}$ contains its fair share of $2^t$ nodes.  Such a digital net is then called a $(t,m,d)$-net.  An infinite sequence of the form \eqref{eq:digitalB} for which this condition holds for all non-negative $m$ is called a  $(t,d)$-sequence.

>>>>

%%Fred's temporary macros
\usepackage[dvipsnames]{xcolor}
\newcommand{\FJHNote}[1]{{\textcolor{ForestGreen}{#1}}}
\newcommand{\NKNote}[1]{{\textcolor{blue}{Nathan: #1}}}
\newcommand{\AGSNote}[1]{{\textcolor{blue}{Aleksei: #1}}}
%\usepackage[normalem]{ulem}

@@

This tutorial describes what qMC is, why we would want to use qMC, and how qMC can be implemented well.  The next section illustrates by example the advantages of qMC.  This is followed by a description of how deterministic LD sequences are constructed (Section \ref{sec:construct}) and randomizations that preserve their low-discrepancy (Section \ref{sec:random}).  We describe various measures of discrepancy (Section \ref{sec:discrepancy}).  We explain how to decide what sample size, $n$, is sufficient to meet the user's error requirements (Section \ref{sec:stop}).  We then discuss how to rewrite the problem of interest in a qMC-friendly way (Section \ref{sec:reformulate}). We briefly discuss applications of qMC beyond computing the mean (Section \ref{sec:beyond}), and finish with a short conclusion (Section \ref{sec:conclusion}). \NKNote{Inevitably, this tutorial is not comprehensive of the full breadth of over a century of development in qMC and uniform distribution theory, dating back to Hermann Weyl's seminal 1916 paper \cite{Wey16}. Instead, our goal is to provide a solid foundation in the core concepts along with practical guidance\FJHNote{, especially for the newcomer}, and to spark further interest and study in the field.}

@@

\FJHNote{Another family of LD sequences that is a generalization of the van der Corput sequence \eqref{eq:vdc} is digital sequences \cite{DicPil10a,Nie92}.  For simplicity, we restrict ourselves to $b = 2$ and let $\oplus$ denote binary digitwise addition modulo $2$ (also known as digitwise exclusive or), e.g., $3/8 \oplus 3/4 = {}_20.011 \oplus {}_20.110 = {}_20.101 = 5/8$.  A digital sequence is defined as
\begin{equation} \label{eq:digital}
	\bsx_i^{\text{dig}} := i_0 \bsx^{\text{dig}} _1 \oplus i_1 \bsx^{\text{dig}}_2 \oplus i_2 \bsx^{\text{dig}} _4 \oplus \cdots \in [0,1)^d \quad \text{for }
	i = i_0 + i_12 + i_2 2^2 + \cdots,
\end{equation}
where $\bsx^{\text{dig}}_1, \bsx^{\text{dig}}_2, \bsx^{\text{dig}}_4, \bsx^{\text{dig}}_8, \ldots$ are carefully chosen to ensure low discrepancy.  (For $d=1$ and $x^{\text{dig}}_{2^m} = 2^{-m-1}$, this is the van  der Corput sequence in base $2$.) The node set $\{ \bsx^{\text{dig}}_0, \ldots, \bsx^{\text{dig}}_{2^m-1}\}$  for non-negative integer $m$ is called a digital net and is closed under $\oplus$.}

\FJHNote{Traditionally, digital nets are defined in terms of $N \times M$ generating matrices, $\mathsf{C}_j$, as follows:
\begin{equation} \label{eq:digitalB}
\renewcommand{\arraystretch}{1.5}
	\begin{pmatrix} x^{\text{dig}}_{i,j,1} \\ x^{\text{dig}}_{i,j,2} \\ \vdots \end{pmatrix}
	= \mathsf{C}_j \begin{pmatrix} i_0 \\ i_1 \\ \vdots \end{pmatrix}
    \quad \pmod{2}, \qquad j = 1,\ldots, d, \ i = 0, 1, \ldots,
\end{equation}
where $x^{\text{dig}}_{i,j,\ell}$ denotes the $\ell^{\text{th}}$ digit of the $j^{\text{th}}$ component of the $i^{\text{th}}$ node.  Here $N$ is the maximum number of bits in the expression for $\bsx^{\text{dig}}_i$, say $52$, and $2^M$ is the maximum number of nodes that is intended to be generated.
It can be seen that definitions  \eqref{eq:digital} and \eqref{eq:digitalB} are equivalent by noting that $\mathsf{C}_j = \bigl(x^{\text{dig}}_{2^m,j,\ell}\bigr)_{\ell,m = 0}^{N,M-1}$.
}

To understand how well these nodes are evenly distributed over $[0,1)^d$, imagine a box of the form
\begin{multline} \label{eq:element_box}
	[a_1 b^{-k_1}, (a_1 + 1) 2^{-k_1}) \times \cdots \times [a_d b^{-k_d}, (a_d + 1) 2^{-k_d}), \\
	a_j \in \{0, \ldots, 2^{k_j} - 1\}, \ k_j \in \{0,1, \ldots \}, \qquad j =1, \ldots d, \ \bsk \in \NN_0.
\end{multline}
This box has volume $2^{-(k_1 + \cdots +k_d)} = 2^{-\lVert\bsk\rVert_1}$.  For a digital net with $2^m$ nodes and $\lVert \bsk \rVert_1 \le m$, a ``fair share" of nodes for this box would be $2^{m- \lVert \bsk \rVert_1}$.  This will occur if and only if
\begin{multline} \label{eq:tcond}
	\text{the first $k_1$ rows of the first $m$ columns of $\mathsf{C}_1$ plus} \\
	\text{the first $k_2$ rows of the first $m$ columns of $\mathsf{C}_2$ plus} \\
	 \vdots \\
	\text{the first $k_d$ rows of the first $m$ columns of $\mathsf{C}_d$} \\
	\text{are linearly independent over addition and multiplication modulo $2$, }
\end{multline}
regardless of the choice of $\bsa = (a_1, \ldots, a_d)$.  The $t$-value of a digital net with $2^m$ nodes is defined as \FJHNote{any} $t$ for which condition \eqref{eq:tcond} holds for all $\bsk$ with $\lVert \bsk \rVert_1 \le m-t$.  Equivalently, \FJHNote{for} this $t$, every box of the form \eqref{eq:element_box} with volume $2^{\lVert \bsk \rVert_1 - m}$ contains its fair share of $2^t$ nodes.  Such a digital net is then called a $(t,m,d)$-net.  An infinite sequence of the form \eqref{eq:digitalB} for which this condition holds for all non-negative $m$ is called a  $(t,d)$-sequence. \FJHNote{Ideally, one would like to construct $(t,m,d)$-nets and $(t,d)$-sequences with $t$ as small as possible.}
